Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-11 paper.tex
trying to get changes
updated paper and documentation

\section{Results and Discussion}

@@

We see that (HOPE IT WORKS WELL OR ELSE...) Most of the further work would be in
optimization. We are trying to measure performance in Python, which is not the
ideal benchmarking language for efficiency and speedups. A port over to C++
using the MPI libraries in C++ rather than the mpi4py libraries in python would
be ideal. Other optimizations mentioned above could also be implemented. To
further explore the Parareal algorithm would involve many test cases and to see
how the Parareal algorithm compares to other approaches---since the actual time
and iterations necessary depend on the system of ODEs to solve.

@@

\textbf{something here about parareal? ashi}

@@

TODO WRITE ABOUT BETTER DATA COLLECTION

\section{Conclusion and Future Work}

>>>>

\section{Experimental Results and Discussion}

@@

We do not see the theoretical speedups and error convergence in our experimental
tests of the Parareal algorithm. In the future, we would like to debug our
implementation of the algorithm and apply it to more complicated systems of ODEs
and more expensive and higher fine operators $g_{\textnormal{fine}}$. We also
would like to test different combinations of $k$ and $Q$ and see how the error
converges after varying step size.

More further work could be in optimization. We are trying to measure performance
in Python, which is not the ideal benchmarking language for efficiency and
speedups. A port over to C++ using the MPI libraries in C++ rather than the
mpi4py libraries in python would be ideal. Other optimizations mentioned above
could also be implemented. To further explore the Parareal algorithm would
involve many test cases and to see how the Parareal algorithm compares to other
approaches---since the actual time and iterations necessary depend on the system
of ODEs to solve.

@@

@@

\section{Conclusion}
